\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-09 paper/main.tex
.

\begin{table*}[!tpb]
  \centering
	\begin{tabular}{|p{2.2cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|}
		\hline
		&\multicolumn{4}{c|}{(a) STITCH results}& \multicolumn{4}{c|}{(b) Yamanishi results}\\
		\hline
		\name{} results&\multicolumn{4}{c|}{PPI graph}&\multicolumn{4}{c|}{PPI graph}\\
		&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}\\
		&Macro AUC&Micro $AUC_p$&Macro AUC&Micro $AUC_p$&Macro AUC&Micro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		MolPred&$0.69$&$0.65$&$0.69$&$0.67$&$0.66$&$0.67$&$0.66$&$0.64$\\
		\hline
		OntoPred&$0.88$&$0.87$&$0.92$&$0.93$&$0.80$&$0.79$&$0.83$&$0.82$\\
		\hline
		\name{} (MolPred + OntoPred) & $0.89$ & $0.90$&$\mathbf{0.93}$&$\mathbf{0.94}$& $0.83$ & $0.82$&$\mathbf{0.84}$&$\mathbf{0.84}$\\
		\hline
	\end{tabular} \medskip

@@

		\hline
		&&\multicolumn{3}{c|}{(c) Yamanishi results}&\multicolumn{3}{c|}{(d) BioSnap results}\\
		Approach&Original&Original scheme&\multicolumn{2}{c|}{Protein split}&Original scheme&\multicolumn{2}{c|}{Protein split}\\

		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.85$& --&--&$0.79$&-- &--\\
		DTINet&DP pairs&$0.91$&$0.74$&$0.67$ & --&--&--\\
		DTIGEMS+&DP pairs&$\mathbf{0.93}$& $0.72$& $0.68$ & --&--&--\\
		DTI-CDF&Proteins&$0.85$&$\mathbf{0.85}$&$0.79$& --&--&--\\
		\hline
		DeepDTI&Drugs& --&--&--&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs& --&--&--&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs& --&--&--&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs& --&--&--&$0.90$&$0.77$&$0.74$\\
		\name&Proteins&$0.84$&$0.84$&$\mathbf{0.84}$&0.85 & $\mathbf{0.85}$& $\mathbf{0.82}$\\
		\hline
	\end{tabular}\medskip

	\caption{(a) + (b) Results for \name{} on STITCH and Yamanishi dataset evaluated with a 5-fold cross-validation. We hereby denote the molecular feature based predictor with \textit{MolPred}, while abbreviating the ontology based, top-down predictor with \textit{OntoPred}. (c) + (d) Results for various state of the art (c) drug--target interaction prediction methods on Yamanishi dataset and (d) drug--target affinity prediction methods on BIOSNAP dataset, evaluated on their original and the protein cross-validation splitting scheme, approximately reproducing the results of MolTrans \textbf{CITATION}.}
	\label{tab:Results}
\end{table*}

@@

>>>>

\begin{table*}

@@

		\hline
		&&\multicolumn{3}{c|}{Yamanishi results}&\multicolumn{3}{c|}{BioSnap results}\\
		Approach&Original&Original scheme&\multicolumn{2}{c|}{Protein split}&Original scheme&\multicolumn{2}{c|}{Protein split}\\

		&Splitting scheme&Macro AUC&Macro AUC&Micro $AUC_p$&Macro AUC&Macro AUC&Micro $AUC_p$\\
		\hline
		Naive predictor&DP pairs&$0.85$& --&--&$0.79$&-- &--\\
		DTINet&DP pairs&$0.91$&$0.74$&$0.67$ & --&--&--\\
		DTIGEMS+&DP pairs&$\mathbf{0.93}$& $0.72$& $0.68$ & --&--&--\\
		DTI-CDF&Proteins&$0.85$&$\mathbf{0.85}$&$0.79$& --&--&--\\
		\hline
		DeepDTI&Drugs& --&--&--&$0.88$&$0.76$&$0.70$\\
		DeepDTA&DP pairs& --&--&--&$0.88$&$0.77$&$0.69$\\
		DeepConv-DTI&DP pairs& --&--&--&$0.88$&$0.76$&$0.73$\\
		MolTrans&DP pairs& --&--&--&$0.90$&$0.77$&$0.74$\\
		\name&Proteins&$0.84$&$0.84$&$\mathbf{0.84}$&0.85 & $\mathbf{0.85}$& $\mathbf{0.82}$\\
		\hline
	\end{tabular}
        \caption{\label{tab:comparison} Comparison of \name{} with
          state of the art drug--target interaction prediction methods
          (Yamanishi dataset) and drug--target affinity prediction
          methods (BioSnap dataset); we evaluated the original and the
          protein-based split in a cross-validation}.
\end{table*}

@@

\begin{table*}[!tpb]
  \centering
  \begin{tabular}{|p{2.2cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|p{0.9cm}|p{0.75cm}|}
    \hline
    &\multicolumn{4}{c|}{(a) STITCH results}& \multicolumn{4}{c|}{(b) Yamanishi results}\\
    \hline
    \name{} results&\multicolumn{4}{c|}{PPI graph}&\multicolumn{4}{c|}{PPI graph}\\
    &\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}&\multicolumn{2}{c|}{without}&\multicolumn{2}{c|}{with}\\
    &Macro AUC&Micro $AUC_p$&Macro AUC&Micro $AUC_p$&Macro AUC&Micro AUC&Macro AUC&Micro $AUC_p$\\
    \hline
    MolPred&$0.69$&$0.65$&$0.69$&$0.67$&$0.66$&$0.67$&$0.66$&$0.64$\\
    \hline
    OntoPred&$0.88$&$0.87$&$0.92$&$0.93$&$0.80$&$0.79$&$0.83$&$0.82$\\
    \hline
    \name{} (MolPred + OntoPred) & $0.89$ & $0.90$&$\mathbf{0.93}$&$\mathbf{0.94}$& $0.83$ & $0.82$&$\mathbf{0.84}$&$\mathbf{0.84}$\\
    \hline
  \end{tabular}
  \caption{\label{tab:Results}Results for \name{} on the STITCH
    and Yamanishi datasets evaluated with 5-fold cross-validation. We 
    call the model using only molecular features
    \textit{MolPred} and the model using only ontology-based
    features \textit{OntoPred}. \name{} combines both types of
    features.}
\end{table*}
